The Geometry of Archaeological Thought: Analysing discplinary change using word embeddings from conference abstracts

### 2020-05-21 documents/paper.Rmd
code tidy in Rmd

```{r read-data}
saa_data <- readxl::read_excel(here::here("data", "raw-data", "saa-abstracts-tally.xlsx"))

# basic stats
library(tidyverse)
abstract_num <- sum(saa_data$number_of_abstracts, na.rm = TRUE)
year_num <- length(which(!is.na(saa_data$number_of_abstracts))) # 41 years

# get all txt files of abstracts
abstract_txt_files <- 
  fs::dir_ls(here::here("data/derived-data/"), 
             recurse = TRUE, 
             regexp = '\\.txt$')
all_txts <- tolower(readtext::readtext(abstract_txt_files))

all_word_counts <- sum(stringi::stri_count_words(all_txts))
```

LW: The data for our study comes from the text of abstracts of oral and poster presentations at the annual meetings of the Society of American Archaeology (SAA). The earliest meeting in our data is 1962, and we have some years missing, especially 1995-2003 where PDF files were not available to us. The total number of abstracts is `r prettyNum(abstract_num, big.mark = ",")` (`r prettyNum(all_word_counts, big.mark = ",")` words) from `r year_num` annual meetings. We obtained PDF files of annual programs from https://www.saa.org/annual-meeting/annual-meeting-archives/program-archives.

@@

>>>>

```{r read-data}
saa_data <- readxl::read_excel(here::here("data", "raw-data", "saa-abstracts-tally.xlsx"))
abstract_num <- sum(saa_data$number_of_abstracts, na.rm = TRUE)
year_num <- length(which(!is.na(saa_data$number_of_abstracts))) # 41 years vs 40
```

LW: The data for our study comes from the text of abstracts of oral and poster presentations at the annual meetings of the Society of American Archaeology (SAA). The earliest meeting in our data is 1962, and we have some years missing, especially 1995-2003 where PDF files were not available to us. The total number of abstracts is `r prettyNum(abstract_num, big.mark = ",")` (xxx words) from `r year_num` annual meetings. We obtained PDF files of annual programs from https://www.saa.org/annual-meeting/annual-meeting-archives/program-archives.

@@

```{r temporal-referencing-plots, cache.extra=tools::md5sum(here::here("006-testing-word-2-vec-temporal-referencing-by-period.R"))}
source(here::here("code/006-testing-word-2-vec-temporal-referencing-by-period.R"))
```
